\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-09 paper/experiments.tex
paper: formatting

\section{Experiments}

To evaluate the performance of our system, we generate plans for queries on two data sets: the American Community Survey and a synthetic dataset.
\subsection{Data sets} \label{subsec:datasets}

@@

\begin{table}
  \centerfloat
  \input{queries}
  \caption{Queries used in our experiments.}
  \label{fig:queries}
\end{table}

>>>>

\section{Experiments}
\todo{we of course need to rewrite this whole section}
To evaluate the performance of our system, we generate plans for queries on two data sets: the American Community Survey and a synthetic dataset.
\subsection{Data sets} \label{subsec:datasets}

@@

\begin{table*}
  \centerfloat
  \input{queries}
  \caption{Queries used in our experiments.}
  \label{fig:queries}
\end{table*}
